\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-07-07 doc/USER_MANUAL/manual_SPECFEM3D.tex
added a reference

\noindent
If you use this new version 2.1, which has non blocking MPI for much better performance for medium or large runs, please cite at least one of these six articles,
in which results of non blocking MPI runs are presented: \cite{PeKoLuMaLeCaLeMaLiBlNiBaTr11,KoErGoMi10,KoViCh10,Kom11,CaKoLaTiMiLeSnTr08,MaKoBlLe08}.\\

>>>>

\noindent
If you use this new version 2.1, which has non blocking MPI for much better performance for medium or large runs, please cite at least one of these six articles,
in which results of non blocking MPI runs are presented: \cite{PeKoLuMaLeCaLeMaLiBlNiBaTr11,KoGoErMi10,KoErGoMi10,KoViCh10,Kom11,CaKoLaTiMiLeSnTr08,MaKoBlLe08}.\\
